### 2021-04-08 papers/SYRCoSE/related.tex
Related work: remove what we said in Intro
SYRCoSE: apply @dmitromikh suggestions
Related work: more grammar

Event structures were introduced by Winskel to study the semantics of 
the calculus of communicating systems~\cite{Winskel:82}. 
Several modifications of event structures~\cite{Langerak:91, Boudol-Castellani:1991}
were later proposed to tackle similar problems.  
To the best of our knowledge, there were no attempts 
to mechanise the classical theory of event structures 
in proof assistants.

More recently event structures were applied 
in the context of relaxed memory models~%
\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19, Moiseenko-al:ECOOP20}.
Among this line of work, we are aware of only one paper~\cite{Moiseenko-al:ECOOP20}
that was accompanied with the mechanisation in a proof assistant. 
The authors formalised \weakestmo~\cite{Chakraborty-Vafeiadis:POPL19} 
memory memory model in \coq. However, this memory model uses 
custom variant of event structures, that does not 
obey axioms of any conventional class of 
event structures~\cite{Winskel:82, Langerak:91, Boudol-Castellani:1991}. 
This fact makes it harder to reuse and adapt it 
for other applications of the theory.

>>>>

Event structures were introduced by Winskel to study the semantics of 
the calculus of communicating systems~\cite{Winskel:82}. 
Several modifications of event structures~\cite{Langerak:91, Boudol-Castellani:1991}
were later proposed to tackle similar problems.

More recently event structures were applied 
in the context of relaxed memory models~%
\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19, Moiseenko-al:ECOOP20}.
Among this line of work, we are aware of only one paper~\cite{Moiseenko-al:ECOOP20}
that was accompanied with a mechanisation in a proof assistant. 
The authors formalised \weakestmo~\cite{Chakraborty-Vafeiadis:POPL19} 
memory memory model in \coq. However, this memory model uses 
a custom variant of event structures, that does not 
obey axioms of any conventional class of 
event structures~\cite{Winskel:82, Langerak:91, Boudol-Castellani:1991}. 
This fact makes it harder to reuse and adapt it 
to other applications of the theory.
